%
% Imports
%
\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{fontawesome}
\usepackage{scrextend}
\usepackage{multicol}
\usepackage{hyperref}
\usepackage{hanging}

%
% Setup
%
\geometry{left=1in, top=.75in, right=1in, bottom=.75in, footskip=.5cm, paperheight=11in, paperwidth=8.5in}
\hypersetup{
  colorlinks=false,
  urlbordercolor=1 1 1
}

\setlength{\parindent}{0in}
\hyphenpenalty=10000
\pagestyle{empty}



%
% Styles
%
\newcommand{\horizontalBreaker}{\ \ \ }
\newcommand{\sectionIndent}{13px}
\newcommand{\sectionEnd}{26px} %used only for itemContent, centers textBox

% Fonts
\newcommand{\primaryFont}{\rmfamily}
\newcommand{\accentFont}{\sffamily}

% Colors
\definecolor{black}{RGB}{0,0,0}
\definecolor{primary}{RGB}{100,130,200}
\definecolor{light}{RGB}{100,100,100}

\newcommand{\sectionHeader}[1]{
  \vspace{3px}
  \accentFont \color{primary} \large
  #1
  \color{black}
  \primaryFont
  \hrulefill
  \vspace{1px}
}

\newcommand{\itemHeader}[3]{
  \vspace{8px}
  \large \textbf{#1}
  \ifx&#3&
    %do nothing
  \else
    \color{primary} \accentFont \normalsize
    \hfill #3
    \color{black} \primaryFont
  \fi

  \ifx&#2&
      %do nothing
  \else
    \vspace{2px}
    \large
    \textit{#2}
  \fi
}

\newcommand{\itemContent}[1]{
  \vspace{1px} \normalsize
  \begin{addmargin}{\sectionIndent}
    #1
    \vspace{1px}
  \end{addmargin}
}

%
% Document
%
\begin{document}

  %
  % Title
  %
  \begin{center}
      {\Huge  \primaryFont Royce Churchill Schultz}\\
          \vspace{6px}
      {\normalsize
          royce.schultz@colorado.edu \horizontalBreaker
          \href{https://www.github.com/royceschultz}{GitHub}, \href{https://linkedin.com/in/royceschultz}{LinkedIn}: royceschultz
      }
  \end{center}

  %
  % Education Section
  %
  \sectionHeader{Education}
  \begin{addmargin}[\sectionIndent]{0px}
    \itemHeader
      {New York University}
      {Tandon School of Engineering}
      {Beginning August 2021}
    \itemContent{Incoming student, M.S. Computer Science}

    \itemHeader
      {University of Colorado, Boulder}
      {College of Engineering}
      {Graduating May 2021}
    \itemContent{B.S. Computer Science, Minor in Applied Mathematics}
    \itemContent{3.7 Major GPA, 3.5 Cumulative GPA}
    \itemContent{Favorite Classes: Big Data Architecture, Machine Learning, Natural Language Processing,\\Advanced Data Science, Computer Vision, Numerical Analysis, Robotics}
  \end{addmargin}

  %
  % Experience Section
  %
  \sectionHeader{Experience}
  \begin{addmargin}[\sectionIndent]{0px}
    \itemHeader{CU Leeds School of Business}{\href{https://github.com/TheBuffsOfWallStreet/NLP-FIN-LAB}{Machine Learning Researcher}}{September 2020 - Present}
    \itemContent{Parsing text from more than 27,000 pages of scanned financial texts using AI vision models.}
    \itemContent{Measuring market sentiment over a corpus of over 100,000 TV News episodes using NLP models.}
    \itemContent{Building distributed data infrastructure to support collaboration for developers working remotely.}
    \itemContent{Supporting many different runtime environments by defining infrastructure using containers.}

    \itemHeader{Amazon}{Software Engineering Intern}{May 2020 - July 2020}
    \itemContent{Used cloud services to build and deploy a web portal to address data needs and security concerns.}
    \itemContent{Wrote efficient algorithms to detect erroneous metrics in a massive data warehouse.}
    \itemContent{Supported continuous integration using automated deployment pipelines and unit tests.}

    \itemHeader{CU Math Academic Resource Center}{Math Tutor}{August 2019 - March 2020}
    \itemContent{Encouraged students to use their critical thinking skills to solve math problems.}
    \itemContent{Held regular office hours, aiding dozens of students each week.}

    \itemHeader{CU Office of Information Technology}{Student Technician}{May 2018 - May 2019}
    \itemContent{Created a web application to increase employee productivity by simplifying daily tasks.}
    \itemContent{Installed and maintained technology systems in rooms across CU’s campus.}

  \end{addmargin}

  %
  % Projects Section
  %
  \sectionHeader{Projects}
  \begin{addmargin}[\sectionIndent]{0px}
    \itemHeader
      {\href{https://github.com/royceschultz/Smart-Garden}{Smart Garden}}
      {}
      {February 2021 - Present}
    \itemContent{Deploying a raspberry pi to control watering cycles and collect metrics like temperature, humidity, and light intensity that are logged wirelessly to an InfluxDB host.}
    \itemContent{Supporting completely remote management with IP cameras, Grafana metric dashboards, and remote control and automation via a web portal.}
  \end{addmargin}

  %
  % Skills Section
  %
  \sectionHeader{Skills}
  \begin{addmargin}[\sectionIndent]{0px}
    \itemContent{\textbf{Languages:} Python, JavaScript, C, C++, Bash, SQL,  MatLab, Scala}
    \itemContent{\textbf{AWS:} EC2, S3, Lambda, RDS, DynamoDB, CloudFormation CDK}
    \itemContent{\textbf{Tools \& Frameworks:} Git, Docker, Docker-Compose, MongoDB, TensorFlow, Scikit-Learn}
    \itemContent{\textbf{Development Methods:} Agile, Unit Testing, Microservices, Containerization, CI/CD}
  \end{addmargin}

\end{document}
